SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-05-03 Chapters/hathor-bitcoin-math.tex
The incredible animal behavior of Dr Linhares

The primary objective of this chapter is to increase our understanding of the Bitcoin through mathematical tools.

@@

@@

Scenario (i) is easy to analyze, because the network would just split and, after a while, both difficulties will be adjusted. Then, they will be just like two different Bitcoin networks.

>>>>

The primary objective of this chapter is to increase the understanding of the Bitcoin through mathematical tools.

@@

Analyze when $k=2$ (for instance, Binance requires only two confirmations for deposits with less than $1,000$).

@@

Scenario (i) is easy to analyze, as the network would split and, after a while, both difficulties will be adjusted. Then, they will be just like two different Bitcoin networks.
